Unsupervised embeddings of organizations capture the latent structure of scientific mobility

### 2020-06-16 paper/current/main.tex

where $M_i$ and $M_j$ are the masses of of the entities, $f\left(d_{ij}\right)$ is a function of the distance, and $G$ is the constant analogous to the gravitational constant in physics. 
In mobility studies, any quantity proportional to the sum of flows from $i$ can be used as $M_i$; a common choice is the population at a point $i$ (e.g., city and country).
For $d_{ij}$, geographical distance is often used. 
We argue that the neural embedding model
Here, we show that the neural embedding model can be interpreted as generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.

@@

The form of Eq.~\ref{eq:flow_gravity_model} maps to the gravity model $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$.
Therefore, we argue that the nerual embedding model is a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
Given flows $T_{ij}$ derived from mobility trajectories, this model attempts to learn the mass $M_i$ and map each entity into more abundant vector space . 
Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

>>>>

where $M_i$ and $M_j$ are the masses of of the entities, $f\left(d_{ij}\right)$ is a function of the distance, and $G$ is the constant analogous to the gravitational constant in physics. 
In mobility studies, any quantity proportional to the sum of flows from $i$ can be used as $M_i$; a common choice is the population at a point $i$ (e.g., city and country).
For $d_{ij}$, geographical distance is often used. 
Here, we show that the neural embedding model can be interpreted as a generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.

@@

The form of Eq.~\ref{eq:flow_gravity_model} maps to the gravity model $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$.
Therefore, we argue that the nerual embedding model can be interpreted as a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
Given flows $T_{ij}$ derived from mobility trajectories, neural embedding model attempts to learn the mass $M_i$, map each entity, and encode the functional distance into more abundant vector space . 
Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
